\documentclass{article}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{array}
\usepackage{makecell}

\renewcommand{\theadfont}{\normalsize\bfseries}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{\thesubsubsection}{1em}{}

\title{System Documentation}
\author{}
\date{}

% Colors for Security Categorizations
\definecolor{navyblue}{RGB}{0,0,128}
\definecolor{lightgray}{RGB}{211,211,211}

\begin{document}

\maketitle

\section{System Description}

\subsection{Purpose and Capabilities}

\subsection{System Components}

\subsubsection{Software Components}

\subsubsection{Third-Party Components/Services}

\subsection{Stakeholders}

\subsection{Operational Environment}

\section{Data Flow Analysis}

\subsection{Data Identification}
\subsubsection{Types of Data Processed}

\subsubsection{Data Classification}

\subsection{Data Flow Diagrams (DFDs)}
\subsubsection{Level 0 (Context Diagram)}
High-level representation of external interactions with ground control, cloud storage, and third-party services.

\subsubsection{Level 1 DFDs}
Detailed flow between onboard sensors, processors, storage, and communication systems.

\subsection{Interfaces}
\subsubsection{Types of Interfaces}

\subsubsection{Protocols \& Security Features}

\section{Security Categorization}

\subsection{Reference Standards}
\begin{itemize}
    \item FIPS 199: Security categorization for federal systems.
    \item NIST SP 800-60: Mapping security categories to information types.
\end{itemize}

\subsection{Impact Levels (Confidentiality, Integrity, Availability)}

% table goes here
\begin{center}
    \rowcolors{2}{lightgray}{white}
    \begin{tabular}{|p{3cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}|}
    \hline
    \rowcolor{navyblue!80}
    \color{white}\textbf{Information Types} & 
    \color{white}\textbf{Confidentiality} & 
    \color{white}\textbf{Integrity} & 
    \color{white}\textbf{Availability} \\ \hline
    
    \makecell{Power Supply/\\Battery} & 
    \makecell[l]{L\\ \scriptsize minimal impact due to 
    \\\scriptsize information only of the 
    \\\scriptsize battery itself } & 
    \makecell[l]{L\\ \scriptsize Due to loss of Integrity }& 
    \makecell[l]{H\\ \scriptsize severe impact to the mission 
    \\\scriptsize can no longer operate
    \\\scriptsize drone without power} \\ \hline
    
    \makecell{Rotors /\\ ECU} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Confidentiality} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Integrity }& 
    \makecell[l]{L
    \\ \scriptsize Due to loss of availability,\\
    \scriptsize severe impact to the mission 
    \\\scriptsize capability} \\ \hline

    \makecell{FILL} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Confidentiality} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Integrity }& 
    \makecell[l]{L
    \\ \scriptsize Due to loss of availability,\\
    \scriptsize severe impact to the mission 
    \\\scriptsize capability} \\ \hline

    \makecell{FILL} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Confidentiality} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Integrity }& 
    \makecell[l]{L
    \\ \scriptsize Due to loss of availability,\\
    \scriptsize severe impact to the mission 
    \\\scriptsize capability} \\ \hline

    \makecell{FILL} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Confidentiality} & 
    \makecell[l]{L
    \\ \scriptsize Due to loss of Integrity }& 
    \makecell[l]{L
    \\ \scriptsize Due to loss of availability,\\
    \scriptsize severe impact to the mission 
    \\\scriptsize capability} \\ \hline

    General-Information & L & L & L \\ \hline

    \rowcolor{lightgray}
    \multicolumn{3}{|l|}{\textbf{System Categorization}} & 
    \cellcolor{lightgray} \\ \cline{1-3}
    & Moderate & High & High \\ \hline
    \end{tabular}
\end{center}
    
\subsection{Overall Categorization}
Overall Information System Impact: \textcolor{navyblue}{\textbf{High}}
    
\subsection{Justification}
The SCADA system's High impact categorization derives from:

\begin{itemize}
\item Critical role in power distribution for military operations
\item Potential for catastrophic consequences including infrastructure failure and loss of life
\item Remote control capabilities affecting physical systems
\item Real-time processing requirements for energy management
\end{itemize}

\section{Risk Management \& Compliance}

Alignment with Risk Management Framework (RMF) per NIST SP 800-37. Categorization informs security control selection (NIST SP 800-53). Ongoing assessment and mitigation per FIPS 200 minimum security controls.

\section{Deliverables}

\begin{itemize}
    \item \textbf{System Description Document}: A comprehensive report covering all aspects outlined in Section 1.
    \item \textbf{Data Flow Diagrams}: Level 0 and Level 1 DFDs with annotations.
    \item \textbf{Security Categorization Whitepaper}: Detailed analysis and justification of the security categorization. See section 4.5 of NIST Special Publication 800-60 Volume I Rev. 1.
\end{itemize}

\end{document}
