\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{soul} % add \st{} for strikthough
\usepackage{siunitx} % add \si{} for SI units
\geometry{a4paper, margin=1in}

\title{Old Updates}
\author{Nick}
\date{\today}

\begin{document}
\maketitle

\par Compares features included in 'AeroTech X9 Drone.pdf' with proposed features in 'AeroTech Pitch.pdf'.

\section{Design and Architecture}
\subsection{Airframe and Physical Characteristics}
\begin{itemize}
    \item \textbf{Materials:} \st{Carbon fiber composite for a lightweight yet robust structure.} Upgrade to military-grade materials for increased resilience against harsh conditions.
    \item \textbf{Dimensions:} Wingspan: 2.5 meters, Length: 1.8 meters, Height: 0.6 meters
    \item \textbf{Weight:} Empty Weight: 12\si{kg}, Max Takeoff Weight: 20\si{kg}.
    \item \textbf{Payload Capacity:} Up to \st{8 kg} 10 kg, supporting modular payloads.
    \item \textbf{\underline{Intelligence Gathering:}} Equip with signals intelligence (SIGINT) and electronic warfare (EW) payloads.
    \item \textbf{\underline{Communications Relay:}} Provide battleﬁeld communication support through relay payloads.
    \item \textbf{\underline{Non-Lethal Countermeasures:}} Integrate systems for electronic countermeasures and area denial.
    \item \textbf{\underline{Anti-Armor and Anti-Personnel Munitions:}} Integrate systems for delivery of ordnance up to 10kg.
    \item \textbf{Aerodynamic Design:} Optimized for stability and efficiency in various flight conditions.
    \item \textbf{\underline{Environmental Sealing:}} Enhance protection against dust, moisture, and electromagnetic interference.
    \item \textbf{\underline{Extended Endurance:}} Incorporate fuel cells or hybrid power systems for longer mission durations.
    \item \textbf{\underline{Secure Storage:}} Secure storage of sensitive data recorded during operations.
\end{itemize}

\subsection{Propulsion System}
\begin{itemize}
    \item \textbf{Engine Type:} Electric brushless motors with high-efficiency propellers.
    \item \textbf{Power Source:} Advanced lithium-polymer batteries with energy densities of 300 Wh/kg.
    \item \textbf{Redundancy:} Dual-motor configuration for enhanced reliability and safety.
\end{itemize}

\subsection{Navigation and Control Systems}
\begin{itemize}
    \item \textbf{Autonomous Navigation:} Integrated AI algorithms for real-time path planning and obstacle avoidance.
    \item \textbf{GPS/GNSS Systems:} Multi-constellation support (GPS, GLONASS, Galileo) for precise positioning.
    \item \textbf{Inertial Measurement Unit (IMU):} High-precision sensors for attitude and heading reference.
    \item \textbf{\underline{Navigation Systems}} Enhanced GNSS with anti-spooﬁng, Inertial Navigation System (INS)
    \item \textbf{Flight Control Software:} Proprietary AeroTech OS with modular architecture for updates and customization.
\end{itemize}

\section{Key Features}

\subsection{High-Resolution Imaging and Sensing}
\begin{itemize}
    \item \textbf{Camera Systems:}
    \begin{itemize}
        \item 4K Ultra-HD optical camera with 30x optical zoom.
        \item \textbf{\underline{Long-Range Zoom:}} Incorporate powerful zoom lenses to identify targets at extended distances.
        \item Thermal imaging sensor for night operations and heat detection.
        \item \textbf{\underline{Night Vision and Thermal Imaging:}} Equip the drone with advanced sensors for 24/7 operational capability.
        \item LIDAR sensor for topographical mapping and obstacle detection.
        \item \textbf{\underline{High-Resolution Imaging:}} Upgrade to military-grade electro-optical/infrared (EO/IR) \linebreak sensors for enhanced reconnaissance.
    \end{itemize}
    \item \textbf{Data Processing:}
    \begin{itemize}
        \item Onboard image processing for real-time analytics.
        \item Supports machine learning algorithms for object recognition and tracking.
    \end{itemize}
\end{itemize}

\subsection{Communication}
\begin{itemize}
    \item \textbf{Communication Channels:}
    \begin{itemize}
        \item Dual-band radio frequency (RF) communication.
        \item 4G/5G cellular connectivity for extended range operations.
        \item Satellite communication module (optional) for beyond-line-of-sight missions.
    \end{itemize}
    \item \textbf{\underline{Communication Links:}} Encrypted RF, SATCOM, LTE/5G.
    \item \textbf{\underline{Beyond-Line-of-Sight (BLOS) Operations:}} Utilize satellite communication modules for extended range missions.
    \item \textbf{Anti-Jamming:} Frequency hopping spread spectrum (FHSS) technology.
    \item \textbf{\underline{Anti-Jamming Technology:}} Integrate frequency hopping and anti-jamming measures to ensure uninterrupted operation.
    \item \textbf{\underline{Data Links:}} Implements robust encryption protocols to protect communications.
\end{itemize}

\subsection{Modular Payload System}
\begin{itemize}
    \item \textbf{Interchangeable Payloads:}
    \begin{itemize}
        \item Delivery containers for logistics and supply chain applications.
        \item Environmental sensors for air quality, radiation, and weather monitoring.
        \item Specialized equipment for agricultural spraying, search and rescue, and surveillance.
    \end{itemize}
    \item \textbf{Quick-Change Mechanism:}
    \begin{itemize}
        \item Tool-less attachment system for rapid deployment.
        \item Automatic payload recognition and configuration.
    \end{itemize}
\end{itemize}

\subsection{Extended Range and Endurance}
\begin{itemize}
    \item \textbf{Flight Time:} Up to 4 hours under standard operating conditions.
    \item \textbf{\underline{Maximum Flight Time:}} Up to 6 hours with hybrid power systems.
    \item \textbf{Range:} Operational range of 200 kilometers, extendable with optional power modules.
    \item \textbf{\underline{Operational Range:}} 300 kilometers (extendable with BLOS ca-pabilities)
    \item \textbf{Energy Efficiency:} Regenerative braking and energy management systems to optimize power consumption.
\end{itemize}

\subsection{Real-Time Data Processing}
\begin{itemize}
    \item \textbf{Onboard Computing:}
    \begin{itemize}
        \item ARMv7 processor capable of handling complex computations.
        \item 64 GB of DDR5 Volatile Storage
        \item 2 TB of NVMe for imagery and mission data retention.
        \item NVIDIA RTX 5000 Embedded GPU
    \end{itemize}
    \item \textbf{Artiﬁcial Intelligence:}
    \begin{itemize}
        \item Machine learning algorithms for anomaly detection and predictive maintenance.
        \item AI-driven decision-making for dynamic mission adjustments.
        \item \textbf{\underline{Autonomous Navigation:}} Reﬁne AI algorithms for obstacle avoidance in contested environments.
        \item \textbf{\underline{Target Recognition:}} Employ machine learning for automatic identiﬁcation and tracking of objects of interest.
        \item \textbf{\underline{Swarm Capabilities:}} Enable coordination between multiple drones for complex mission execution.
    \end{itemize}
\end{itemize}

\section{Operational Capabilities}
\subsection{Versatile Applications}
The AeroTech X9 is designed for a multitude of applications:
\begin{itemize}
    \item \textbf{Infrastructure Inspection:} Bridges, pipelines, power lines, and wind turbines.
    \item \textbf{Agricultural Monitoring:} Crop health analysis, irrigation management, and yield estimation.
    \item \textbf{Disaster Response:} Rapid assessment of affected areas, search and rescue support.
    \item \textbf{Logistics and Delivery:} Transporting medical supplies, packages, and critical equipment.
\end{itemize}

\subsection{Environmental Adaptability}
\begin{itemize}
    \item \textbf{Altitude Range:} Operational ceiling of 5,000 meters above sea level.
    \item \textbf{\underline{Maximum Altitude}} 6,000 meters above sea level.
    \item \textbf{Wind Resistance:} Stable flight in winds up to 35 km/h.
    \item \textbf{\underline{Environmental Tolerance:}} Operational in temperatures from $-30^\circ$C to $55^\circ$C, wind resistance up to 45 km/h.
\end{itemize}

\section{Safety and Compliance}
\subsection{Safety Features}
\begin{itemize}
    \item \textbf{Redundant Systems:} Backup sensors and control systems to prevent failures.
    \item \textbf{Obstacle Avoidance:} 360-degree sensing and avoidance capabilities.
    \item \textbf{Emergency Protocols:}
    \begin{itemize}
        \item Automatic return-to-home (RTH) function upon signal loss or low battery.
        \item Geo-fencing to prevent entry into restricted areas.
    \end{itemize}
\end{itemize}

\subsection{Regulatory Compliance}
\begin{itemize}
    \item \textbf{Certiﬁcation:} Meets FAA, EASA, and other international aviation authority standards.
    \item \textbf{Emission Standards:} Zero-emission electric propulsion aligns with environmental guidelines.
\end{itemize}

\section{User Interface and Control}
\subsection{Ground Control Station (GCS)}
\begin{itemize}
    \item User-Friendly Interface: Intuitive controls with customizable layouts.
    \item Mission Planning Software: Advanced tools for route planning, waypoint management, and mission simulation.
    \item Real-Time Monitoring: Live video feed, telemetry data, and system status updates.
\end{itemize}

\subsection{Remote and Autonomous Operation}
\begin{itemize}
    \item Remote Piloting: Manual control options for precise maneuvering.
    \item Autonomous Missions: Pre-programmed missions with the ability to adapt to changing conditions.
    \item Swarm Capability: Coordination with multiple drones for complex operations.
\end{itemize}

\section{Maintenance and Support}
\subsection{Ease of Maintenance}
\begin{itemize}
    \item Modular Design: Simpliﬁes repairs and component replacements.
    \item Diagnostic Tools: Onboard diagnostics and remote health monitoring.
    \item Maintenance Alerts: Predictive alerts for scheduled maintenance activities.
\end{itemize}

\subsection{Training and Support Services}
\begin{itemize}
    \item Pilot Training Programs: Comprehensive courses for operators and technicians.
    \item Customer Support: 24/7 technical assistance and ﬁeld support teams.
    \item Documentation: Detailed user manuals, maintenance guides, and online resources.
\end{itemize}

\section{Compliance and Certifications}
\begin{itemize}
    \item Regulatory Compliance: Designed to meet defense regulatory standards and airworthiness requirements.
    \item Cybersecurity Standards: Adherence to NIST and ISO cybersecurity frameworks to safeguard against cyber threats.
    \item Export Controls: Compliance with International Traﬃc in Arms Regulations (ITAR) and other export control laws.
\end{itemize}

\end{document}